Impact of LAIV on School Absenteeism

### 2016-09-20 paper.Rmd
another chart for parker

```{r}
temp <-
  df %>%
  filter(flu_season) %>%
  group_by(school, grade) %>%
  summarise(absences = length(which(absent)),
            vaccinations = length(unique(id[vaccine])),
            students = length(unique(id)),
            eligibles = n()) %>%
  mutate(immunization_rate = vaccinations / students * 100,
         absenteeism_rate = absences / eligibles * 100) %>%
  rename(Grade = grade,
         Students = students)

@@

g <- ggplot(data = temp,
       aes(x = immunization_rate,
           y = absenteeism_rate)) +
  geom_point(aes(size = Students,
             color = Grade),
             alpha = 0.6) +
  xlab('Immunization rate') +
  ylab('Absenteeism rate') +
  theme_economist() +
  ggtitle('Association between immunization and flu season absenteeism',
          'Each dot represents one grade at one school') +
  ylim(0, 20)
print(g)
ggsave('~/Desktop/chart_for_parker.pdf')
print(g + scale_y_log10())

>>>>

```{r}
temp <-
  df %>%
  group_by(school, grade) %>%
  summarise(absences = length(which(absent[flu_season])),
            non_flu_absences = length(which(absent[!flu_season])),
            vaccinations = length(unique(id[vaccine])),
            students = length(unique(id)),
            eligibles = length(id[flu_season]),
            non_flu_eligibles = length(id[!flu_season])) %>%
  mutate(immunization_rate = vaccinations / students * 100,
         absenteeism_rate = absences / eligibles * 100,
         non_flu_absenteeism_rate = non_flu_absences / non_flu_eligibles * 100) %>%
  rename(Grade = grade,
         Students = students)

@@

# Get increase in absenteeism in flu season
temp$increase <- temp$absenteeism_rate - temp$non_flu_absenteeism_rate

g <- ggplot(data = temp,
       aes(x = immunization_rate,
           y = increase)) +
  geom_point(aes(size = Students,
             color = Grade),
             alpha = 0.6) +
  xlab('Immunization rate') +
  ylab('Increase in absenteeism during flu season') +
  theme_economist() +
  ggtitle('Association between immunization and excess absenteeism during flu season',
          'Each dot represents one grade at one school') +
  geom_hline(yintercept = 0, color = 'red', alpha = 0.6)
print(g)
ggsave('~/Desktop/chart_for_parker.pdf')
print(g + scale_y_log10())
```

The below chart shows the same, but by school.

```{r}

temp <-
  df %>%
  group_by(school) %>%
  summarise(grades = paste0(sort(unique(grade)), collapse = ','),
            absences = length(which(absent[flu_season])),
            non_flu_absences = length(which(absent[!flu_season])),
            vaccinations = length(unique(id[vaccine])),
            students = length(unique(id)),
            eligibles = length(id[flu_season]),
            non_flu_eligibles = length(id[!flu_season])) %>%
  mutate(immunization_rate = vaccinations / students * 100,
         absenteeism_rate = absences / eligibles * 100,
         non_flu_absenteeism_rate = non_flu_absences / non_flu_eligibles * 100) %>%
  rename(Students = students) %>%
  mutate(Type = ifelse(grepl('PK|KG|2,3,4', grades), 'Elementary',
                       ifelse(grepl('6,7|7,8', grades), 'Middle',
                              ifelse(grepl('10|11|12', grades), 'High', NA))))

# Get increase in absenteeism in flu season
temp$increase <- temp$absenteeism_rate - temp$non_flu_absenteeism_rate

g <- ggplot(data = temp,
       aes(x = immunization_rate,
           y = increase,
           group = Type)) +
  geom_point(aes(size = Students,
             color = Type,
             pch = Type),
             alpha = 0.6) +
  xlab('Immunization rate') +
  ylab('Increase in absenteeism during flu season') +
  theme_economist() +
  ggtitle('Association between immunization and excess absenteeism during flu season',
          'Each dot represents one grade at one school') +
  geom_hline(yintercept = 0, color = 'red', alpha = 0.6)
print(g)
ggsave('~/Desktop/chart_for_parker.pdf',
       width = 11,
       height = 8.5,
       units = 'in')
print(g + scale_y_log10())
```
